opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-22 chapters/04_our_dataset.tex
Removed mention of second HKUST dataset which is unpublishable

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiments, some of them labeled with corresponding structural information. The following paragraphs detail the contribution of each research group. Most data was collected using \ce{Cu} radiaton sources which have a  $K_{\alpha1}$ wavelength of $\lambda=1.54056\text{\AA}$ and a $K_{\alpha2}$ wavelength of $\lambda=1.54439\text{\AA}$. We filtered the submitted datasets to exclude patterns with invalid features such as the pattern containing only one unique recorded angle or negative angles, the pattern containing less than 50 recorded angles total, or all intensities being zero. \\

The below Table$\eqref{tab:merged}$ provides an overview of the opXRD database. The availability of the chemical composition, spacegroups, lattice parameters, and atomic coordinates of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``Atom coords.'' respectively.

\begin{table}[!htb]
\centering
\caption{The opXRD database}
\label{tab:merged}
\scalebox{0.81}{
\begin{adjustbox}{center}
\begin{tabular}{@{}lllllll@{}}
\toprule
\textbf{Institution} & \textbf{No. patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Atom coords.} & \textbf{Research Project} \\
\midrule
CNRS        &  1052          & \cmark   & \partialcheck{85}   & \cmark   &  \partialcheck{85}   & Extracted from the COD \\ 
HKUST(GZ)   &  21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         &  338          & \cmark   & \cmark   & \partialcheck{90}   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        &  790          & \cmark   & \partialcheck{63}   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         &  19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        &  64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        &  n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}
\end{adjustbox}}
\end{table}

@@

A small-scale experimental powder X-ray database called the X-Ray Phase Identification Public Experimental Dataset (XRed) was established over the past two years.\footnote{XRed can be accessed on GitHub at \url{https://github.com/WPEM/XRED}.} The primary objective of this database is to support the development of intelligent phase identification technology, serving as a foundation for data collection for future large-scale machine learning calculations. \\

The data in XRed were generated in our laboratory using instruments such as the Empyrean 3.0, Aeris, and Bruker D8 Advance diffractometers, all utilizing \ce{Cu} X-ray sources. Hundreds of pXRD patterns have been obtained through XRD refinement, enabling the determination of detailed lattice constants, atomic sizes, and other structural parameters. These patterns are labeled with CIF files that document the refined structures. The dataset is organized by elemental systems and includes original experimental files ranging from single-phase to five-phase mixtures, as well as mixtures studied for different tasks. \\

Additionally, Xqueryer,\footnote{Xqueryer can be accessed at \url{https://xqueryer.caobin.asia/}.} a cutting-edge free online platform for intelligent structure identification has been launched. Users can upload experimental pXRD data to identify crystal structures and extract all relevant information available in the Materials Project database\cite{jain2013commentary}. Uploaded data are securely stored and integrated into the comprehensive opXRD database to progress toward a large-scale, long-term experimental resource. All usage complies with Xqueryer's terms of service.

@@

Each combinatorial Zn–V–N library was synthesized using radio-frequency co-sputtering of Zn and V in a mixed Ar and \ce{N2} plasma. An orthogonal deposition temperature and composition gradient was created, resulting in a deposition temperature of $220\degree$C for samples 1~–~9 and $114\degree$C for samples 37~–~45. The composition for each sample was determined using X-ray fluorescence (XRF) spectroscopy which was further calibrated through Rutherford backscattering spectroscopy (RBS) based on selected samples. The newly identified and isolated semiconductor \ce{Zn2VN3} was identified to exhibit a cation-disordered wurtzite structure as verified by additional GI-XRD and SAED measurements\cite{Zhuk2021}. \\
Tin halide perovskites were deposited using single-step spin-coating as reported elsewhere\cite{Wieczorek2023}. Methylammonium lead iodide libraries with varying degrees of residual \ce{PbI2} were deposited using a two-step procedure involving both thermal evaporation of \ce{PbI2} and subsequent spin-coating of a methylammonium solution. The relative phase fractions were quantified using supplementary azimuthal angle scans coupled with structural factors and geometrical factors as reported elsewhere\cite{Wieczorek2024}. Fully inorganic lead perovskite libraries were prepared using thermal co-evaporation of lead and cesium halide salts.
All metal halide perovskite libraries were measured within a custom-made X-Ray transparent inert-gas dome, resulting in the presence of minor additional features within the $\theta=19 \text{–}31\degree$ range. For all combinatorial libraries where any phases are specified, the complete set of phases is reported in the metadata. \\

@@

A major part of the research focused on high-entropy materials, which involved incorporating many different elements into single-phase structures, leading to peak shifts or phase separations. Most of those multi-component complex materials appeared in various structures, including rock-salt, spinel, fluorite, perovskite, and delafossite. The samples were prepared either in powder or in bulk form; therefore, powder XRD was performed on samples with adjusted height. The samples were prepared using various synthesis techniques, mostly solid-state or wet chemical syntheses, to obtain the desired structures. Consequently, particle size and crystallinity varied significantly. The sample set also includes samples that were not successfully measured or where phases could not be identified. \\

>>>>

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiments, some of them labeled with corresponding structural information. The following paragraphs detail the contribution of each research group. Most data was collected using \ce{Cu} radiaton sources which have a  $K_{\alpha1}$ wavelength of $\lambda=1.54056\text{\AA}$ and a $K_{\alpha2}$ wavelength of $\lambda=1.54439\text{\AA}$. We filtered the submitted datasets to exclude patterns with invalid features such as the pattern containing only one unique recorded angle or negative angles, the pattern containing less than 50 recorded angles total, or all intensities being zero. The below Table$\eqref{tab:merged}$ provides an overview of the opXRD database.

\begin{table}[!htb]
\centering
\caption{\footnotesize The opXRD database: The availability of the chemical composition, spacegroups, lattice parameters, and atomic coordinates of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``Atom coords.'' respectively.}
\label{tab:merged}
\scalebox{0.79}{
\begin{adjustbox}{center}
\begin{tabular}{@{}lllllll@{}}
\toprule
\textbf{Institution} & \textbf{No. patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Atom coords.} & \textbf{Research Project} \\
\midrule
CNRS        &  1052          & \cmark   & \partialcheck{85}   & \cmark   &  \partialcheck{85}   & Diffraction data extracted from the COD \\ 
HKUST(GZ)   &  21          & \cmark   & \cmark   & \cmark   & \cmark   & Phase/structure identification dataset  \\ 
USC         &  338          & \cmark   & \cmark   & \partialcheck{90}   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        &  790          & \cmark   & \partialcheck{63}   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N libraries \\ 
INT         &  19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        &  64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        &  n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Perovskites precursors, Mn-Sb-O system  \\ 
\bottomrule
\end{tabular}
\end{adjustbox}}
\end{table}

@@

A small-scale experimental powder X-ray database called the X-Ray Phase Identification Public Experimental Dataset (XRed) was established over the past two years.\footnote{XRed can be accessed on GitHub at \url{https://github.com/WPEM/XRED}.} The primary objective of this database is to support the development of intelligent phase identification technology, serving as a foundation for data collection for future large-scale machine learning calculations. The XRed dataset primarily focuses on metal and metal-oxide particles, with data generated using instruments such as the Empyrean 3.0, Aeris, and Bruker D8 Advance diffractometers, all utilizing \ce{Cu} X-ray sources. Hundreds of pXRD patterns have been obtained through XRD refinement, enabling the determination of detailed lattice constants, atomic sizes, and other structural parameters. These patterns are labeled with CIF files that document the refined structures. The dataset is organized by elemental systems and includes original experimental files ranging from single-phase to five-phase mixtures, as well as mixtures studied for different tasks. \\

Xqueryer,\footnote{Xqueryer can be accessed at \url{https://xqueryer.caobin.asia/}.} a recently launched cutting-edge free online platform for intelligent structure identification, will also serve as a source of data for the opXRD database. Users can upload experimental pXRD data to identify crystal structures and extract all relevant information available in the Materials Project database\cite{jain2013commentary}. Uploaded data are securely stored and integrated into the comprehensive opXRD database to progress toward a large-scale, long-term experimental resource. All usage complies with Xqueryer's terms of service.

@@

Combinatorial Zn–V–N libraries were synthesized using radio-frequency co-sputtering of Zn and V in a mixed Ar and \ce{N2} plasma. An orthogonal deposition temperature and composition gradient was created, resulting in a deposition temperature of $220\degree$C for samples 1~–~9 and $114\degree$C for samples 37~–~45. The composition for each sample was determined using X-ray fluorescence (XRF) spectroscopy which was further calibrated through Rutherford backscattering spectroscopy (RBS) based on selected samples. The newly identified and isolated semiconductor \ce{Zn2VN3} was identified to exhibit a cation-disordered wurtzite structure as verified by additional GI-XRD and SAED measurements\cite{Zhuk2021}. \\
Tin halide perovskites were deposited using single-step spin-coating as reported elsewhere\cite{Wieczorek2023}. Methylammonium lead iodide libraries with varying degrees of residual \ce{PbI2} were deposited using a two-step procedure involving both thermal evaporation of \ce{PbI2} and subsequent spin-coating of a methylammonium solution. The relative phase fractions were quantified using supplementary azimuthal angle scans coupled with structural factors and geometrical factors as reported elsewhere\cite{Wieczorek2024}. Fully inorganic lead perovskite libraries were prepared using thermal co-evaporation of lead and cesium halide salts. All metal halide perovskite libraries were measured within a custom-made X-Ray transparent inert-gas dome, resulting in the presence of minor additional features within the $\theta=19 \text{–}31\degree$ range. For all combinatorial libraries where any phases are specified, the complete set of phases is reported in the metadata. \\

@@

X-ray diffraction data was collected from a wide range of research projects conducted at the Institute of Nanotechnology over the past years. A major part of the research focused on high-entropy materials, which involved incorporating many different elements into single-phase structures, leading to peak shifts or phase separations. Most of those multi-component complex materials appeared in various structures, including rock-salt, spinel, fluorite, perovskite, and delafossite. The samples were prepared either in powder or in bulk form; therefore, powder XRD was performed on samples with adjusted height. The samples were prepared using various synthesis techniques, mostly solid-state or wet chemical syntheses, to obtain the desired structures. Consequently, particle size and crystallinity varied significantly. The sample set also includes samples that were not successfully measured or where phases could not be identified. \\
